Introducing statistics with `intRo`

### 2016-01-08 jcgs-paper-2016/paper.Rmd
Start on the modules section

## Modules
TODO: Rewrite this as the details behind the modularity. Add information on writing your own modules

>>>>

## Modules
An \texttt{intRo} module is a set of self-contained executible R scripts that together produce a set of introductory statistics functionality. \texttt{intRo} modules were designed in this way to allow for simple dynamic creation of the user interface at run-time, as well as ease the process of converting existing analysis code to the \texttt{intRo} framework. In this section, we detail the structure of these modules, and the process of creating and deploying new modules.

A module consists of the following scripts:

* *helper.R* - R code that performs some statistical analysis or transformation. This would typically be in the form of a function, and similar to any standard R script.
* *libraries.R* - Code to load any libraries which are not part of core R.
* *observe.R* - Shiny observer code typically used to update choices of an input box.
* *output.R* - Shiny output code defining the results of the analysis that should be displayed to the user.
* *reactive.R* - Shiny reactives, typically containing data that depend on inputs.
* *ui.R* - Shiny user interface definition, including the placement of the inputs and outputs.

The modules provided with \texttt{intRo} are contained in the modules folder. The top level directory in the modules folder defines the category of the module (currently `data`, `summaries`, or `statistics`). Within each of these categories is a folder named according to the name of the module. This folder houses the previously defined scripts. As an example, we will walk through the contents of the `contingency` module.

Since the `contingency` module performs a statistical analysis, it is part of the statistics category, and hence can be found in the \texttt{intRo} repository at **modules/statistics/contingency**. Let's first examine *helper.R*:

```{r, eval=FALSE}
cont.table <- function(intro.data, x, y, type, digits) {  
    interpolate(
        ~ (my.tbl <- cbind(rbind(table(df$y, df$x), 
                      Total = colSums(table(df$y, df$x))), 
                Total = c(rowSums(table(df$y, df$x))[-(length(df$x))], sum(table(df$y, df$x))))),
        df = quote(intro.data),
        x = x,
        y = y,
        mydir = userdir,
        `_env` = environment(),
        file = "code_contingency.R"
    )

    if (type == "totalpercs") interpolate(~(my.tbl <- my.tbl / sum(table(df$y, df$x))), 
                                          df = quote(intro.data), x = x, y = y,  
                                          mydir = userdir, `_env` = environment(), 
                                          file = "code_contingency.R", append = TRUE)
    if (type == "rowpercs") interpolate(~(my.tbl <- t(apply(my.tbl[-nrow(my.tbl),], 1, 
                                                            function(row){row / row[ncol(my.tbl)]}))),  
                                        mydir = userdir,`_env` = environment(), 
                                        file = "code_contingency.R", append = TRUE)
    if (type == "columnpercs") interpolate(~(my.tbl <- apply(my.tbl[,-ncol(my.tbl)], 2, 
                                                             function(col){col / col[nrow(my.tbl)]})),  
                                           mydir = userdir, `_env` = environment(), 
                                           file = "code_contingency.R", append = TRUE)

    if (type %in% c("totalpercs", "rowpercs", "columnpercs")) interpolate(~(new.digits <- digits), 
                                                                          digits = digits, mydir = userdir,
                                                                          `_env` = environment(), 
                                                                          file = "code_contingency.R", 
                                                                          append = TRUE)
    else interpolate(~(new.digits <- 0),  mydir = userdir, `_env` = environment(), 
                     file = "code_contingency.R", append = TRUE)

    interpolate(~(format(round(my.tbl, digits = new.digits))), mydir = userdir, `_env` = environment(), 
                file = "code_contingency.R", append = TRUE)
}
```
